
In this section, we will search for emission in the phase range between
the peaks of the pulsar's light curve. This potential DC emission could originate
in the pulsar's winds, from inside the pulsar's magnetosphere, or 
the emission could be spatially coincidental but physically
unrealted to the pulsar.

The \gev emission in the off-peak from LAT-detected pulsars has been studied in several previous 
publications. In particular, the spatially-extended \velax pulsar wind nebula has
been detected by the LAT in the off-peak phase region of the Vela pulsar \citep{LAT_collaboration_Vela_X_2010}
and the Crab nebula has been detected by the LAT \citep{LAT_collaboration_crab_2010}.
Surprisingly, this \gev emission from the Crab nebula was found to be variable
in time \citep{LAT_Collaboration_Crab_Flare_2011}.

Most prominently, a dedicated analysis was performed using LAT data of
the off-peak emission of 54 LAT-detected pulsars using 16 months of survey observations
\citep{LAT_collaboration_PWNCAT_2011}. 
The search discovered ten pulsars wich significant off-peak emission.
Along with \velax and the Crab nebula, the 
search discovered a source coincident with the TeV source HESS\;J1023-575
in the off-peak window of PSR\;J1023-5746. In addtion, four of hte other
regions showed a significantly cutoff pulsar-like spectrum and are
suspected to be be of magnetospheric origin.

We expand upon this previous work by searching in the off-peak region
of all 107 pulsars presented in this catalog. In addition to the larger
list of pulsars, in this earch we use an expanded data set, a larger energy range,
and an improved analysis method.
